Boutiques: a flexible framework for automated application integration in computing platforms

### 2016-12-19 paper.tex
added affiliation

\author{Tristan Glatard, Tristan Aumentado-Armstrong, Natacha Beck, Pierre Bellec,\\
        Remi Bernard, Sorina Camarasu-Pop, Fr\'ed\'eric Cervenansky, Samir Das, \\
        Rafael Ferreira da Silva, Guillaume Flandin, John Flavin, Pascal Girard, \\
        Krzysztof J. Gorgolewski, Gregory Kiar, Charles G. Guttmann, Nathaniel Kofalt, \\
        Pierre-Olivier Quirion, Pierre Rioux, Marc-\'Etienne Rousseau, Gunnar Schaeffer, Alan C. Evans}

\maketitle

@@

Finally, a JSON editor facilitates the writing of \boutiques manifests
through a web interface.

>>>>

\author{Tristan Glatard, Tristan Aumentado-Armstrong, Natacha Beck, Pierre Bellec,\\
        Remi Bernard, Sorina Camarasu-Pop, Fr\'ed\'eric Cervenansky, Samir Das, \\
        Rafael Ferreira da Silva, Guillaume Flandin, John Flavin, Pascal Girard, \\
        Krzysztof J. Gorgolewski, Gregory Kiar, Charles G. Guttmann, Nathaniel Kofalt, \\
        Pierre-Olivier Quirion, Pierre Rioux, Marc-\'Etienne Rousseau, Gunnar Schaeffer, Alan C. Evans}
\note{greg}{gk's affiliation: Department of Biomedical Engineering, Johns Hopkins University, Baltimore, MD}
\maketitle

@@

Finally, a JSON editor facilitates the writing of \boutiques manifests
through a web interface and a Jupyter Notebook tutorial facilitates
new users getting started with Boutiques..
